---
title: "Interesting Title"
author: "Team"
date: "19/10/2020"
output: html_document
abstract: "Do abstract"
---

```{r}
#install.packages("tidyverse")
#install.packages("brms")
library(tidyverse)
library(brms)
```


```{r}
# read in gss 2017

gss <- read_csv("inputs/gss.csv")
```


# Introduction

# Results

```{r}
# filtering down what columns we plan to use

gss <- gss %>% 
  mutate(born_canada = ifelse(place_birth_canada == "Born in Canada", 1, 0))

planned_cols <- gss %>% select(
  age, age_first_child, age_start_relationship, 
  age_at_first_marriage, age_at_first_birth, feelings_life, sex, place_birth_canada,
  place_birth_macro_region, province, pop_center, marital_status, vis_minority, 
  education, own_rent, living_arrangement, average_hours_worked, self_rated_health,
  self_rated_mental_health, regilion_importance, income_respondent, income_family,
  number_marriages, born_canada
)

planned_cols2 <- planned_cols %>% select(
  age, feelings_life, sex, province, marital_status, education, own_rent,
  average_hours_worked, self_rated_mental_health, self_rated_health, 
  regilion_importance, income_family, number_marriages, born_canada
)

planned_cols3 <- planned_cols2 %>% select(
  feelings_life, sex, income_family, self_rated_mental_health,
  marital_status, age, born_canada
)

#planned age groups for now: 15-35, 35-65, 65+

test <- planned_cols3 %>% 
  drop_na(self_rated_mental_health) %>% 
  filter(self_rated_mental_health != "Don't Know") %>% 
  mutate(happy = ifelse(feelings_life > 5, 1, 0),
         mental_health = ifelse(self_rated_mental_health == "Excellent", 5,
                                ifelse(self_rated_mental_health == "Very Good", 4,
                                       ifelse(self_rated_mental_health == "Good", 3,
                                              ifelse(self_rated_mental_health == "Fair", 2, 1)))))


model <- brm(happy ~ born_canada + income_family
             + self_rated_mental_health + groups_age, data = test, family = bernoulli(),
             seed = 21)
```

# Discussion

## Analysis

## Weaknesses and Next Steps

# Appendicies

## Citations

- R Core Team (2019). R: A language and environment for statistical computing. R Foundation for
  Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.

- Paul-Christian Bürkner (2017). brms: An R Package for Bayesian Multilevel Models Using Stan.
  Journal of Statistical Software, 80(1), 1-28. doi:10.18637/jss.v080.i01

- Paul-Christian Bürkner (2018). Advanced Bayesian Multilevel Modeling with the R Package brms.
  The R Journal, 10(1), 395-411. doi:10.32614/RJ-2018-017
  
- JJ Allaire and Yihui Xie and Jonathan McPherson and Javier Luraschi and Kevin Ushey and Aron
  Atkins and Hadley Wickham and Joe Cheng and Winston Chang and Richard Iannone (2020).
  rmarkdown: Dynamic Documents for R. R package version 2.3. URL https://rmarkdown.rstudio.com.

- Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43),
  1686, https://doi.org/10.21105/joss.01686
  
  
  
  