---
title: "Interesting Title"
author: "Team"
date: "19/10/2020"
output: html_document
abstract: "Do abstract"
---

```{r, echo = F, warning=F, message=F}
#install.packages("tidyverse")
install.packages("gtsummary")
library(tidyverse)
library(gtsummary)
```


```{r, echo = F, warning=F, message=F}
# read in gss 2017
gss <- read_csv("inputs/gss.csv")
```


# Introduction

# Data

```{r, echo=F}
# filtering down what columns we plan to use

gss <- gss %>% 
  mutate(born_canada = ifelse(place_birth_canada == "Born in Canada", 1, 0))

used_cols <- gss %>% select(
  age, age_first_child, age_start_relationship, 
  age_at_first_marriage, age_at_first_birth, feelings_life, sex, place_birth_canada,
  place_birth_macro_region, province, pop_center, marital_status, vis_minority, 
  education, own_rent, living_arrangement, average_hours_worked, self_rated_health,
  self_rated_mental_health, regilion_importance, income_respondent, income_family,
  number_marriages, born_canada, education
)

planned_cols2 <- planned_cols %>% select(
  age, feelings_life, sex, province, marital_status, education, own_rent,
  average_hours_worked, self_rated_mental_health, self_rated_health, 
  regilion_importance, income_family, number_marriages, born_canada, education,
  age_at_first_marriage
)

planned_cols3 <- planned_cols2 %>% select(
  feelings_life, sex, income_family, self_rated_mental_health,
  marital_status, age, born_canada, self_rated_health, average_hours_worked, education,
  age_at_first_marriage
)

gss2 <- gss %>% 
  mutate(only_highschool = ifelse(grepl("high school", education, ignore.case = T), 1, 0),
         minority = ifelse(vis_minority == "Not a visible minority", 1, 0))
gss2 <- gss2 %>% 
  mutate(rent = ifelse(own_rent == "Rented, even if no cash rent is paid", 1, 0))

gss2 %>% group_by(vis_minority) %>% 
  summarise(n = n())

planned_cols3 <- planned_cols3 %>% 
  mutate(level_of_ed = ifelse(grepl("high school", education, ignore.case = T), 1, 0)) 
```

# Model

We plan to run a logistic regression model in the form:

$$Pr(y_i = 1) = logit^{-1} \left( \alpha^{marriage}_{m[i]} + \alpha^{income}_{i[i]} + \alpha^{gender}_{g[i]} + \alpha^{children}_{c[i]} + \alpha^{rent}_{r[i]}\right)$$
where each $\alpha$ refers to self rated health and mental health, age and whether the person is born in Canada. The notation $i[i]$ refers to a person's individual income, $r[i]$ represent whether a person is renting their house or not, $g[i]$ represents a person's gender, for this scenario it has been restricted to male/female and lastly, .

The value we want to predict is whether or not someone has had a higher education, more specifically, we restrict it to a variable which gives a 1 for if a person has only completed high school and a 0 if they've completed some other level of education.

This model was run using the glm. The glm function was run with the family being specified as binomial() because our response variable "only_highschool" is a binary variable with responses of "yes" or "no".

The ouput of our model gives us a probability of whether someone has only completed high school. 

Figure 1
```{r}
# run the model with feeling of life as the response, born in canada, mental health, 
# and age being the predictors

gss2 <- gss2 %>% 
  mutate(married = ifelse(marital_status == "Married", 1, 0))

gss_logit <- glm(only_highschool ~ number_total_children_known +
                   sex + income_respondent + rent + married,
                 data = gss2, family = binomial())
summary(gss_logit)
logit_summary <- broom::tidy(gss_logit, conf.int = T)
logit_summary
#gtsummary::tbl_regression(gss_logit, intercept = T)
```

Using the glm() function, our logit function is:

$$log \left( \frac{\hat{p}}{1-\hat{p}} \right) = -1.52 - .5*x_{children}
- .455*x_{male} +-.147*x_{income > 125000} + 1.5*x_{income_{25000-49999}} + \\ .76*x_{income_{50000 - 74999}} + .265*x_{income_{75000-99999}} + 2.22*x_{income_{< 25000}} + .61*x_{marraige} + .116*x_{rent}$$

The output of this model is not like other regressions where we plug in numbers and receive our value right away, we have to do a little more work for this one. Every term in this equation will either be multiplied by 1 or 0, if the person has that characteristic or not. You may notice that some categories are missing, such as the female gender, income from 100000-124999 dollars and not born in Canada. These are missing becuase the function takes the other values as default ideal values, so for every difference in the category, the probability of having only a high school diploma, goes down.


```{r}
# get summary and plot coefficients
logit_summary %>% ggplot(aes(term, estimate)) + geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                width = .5, colour = "red") +
  geom_hline(aes(yintercept = 0), color = "black", linetype = "dashed") +
  coord_flip() + 
  labs(title = "Distribution of Estimation of Coefficients",
       subtitle = "Red bars represent estimated error",
       y = "Weight",
       x = "Estimate",
       caption = "Source: GSS 2017 Data")
```

This graph shows the distribution of coefficients for each variable covered, with the standard error extended to the left and right. There is a bar in the middle of the graph (at x = 0), to help visualize whether the variable has increases the probability of a person only completing high school.

Figure 3
```{r}
gtsummary::tbl_regression(gss_logit, intercept = T)
```


# Discussion

## Analysis

## Weaknesses and Next Steps

# Appendicies

## Citations

- R Core Team (2019). R: A language and environment for statistical computing. R Foundation for
  Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.
  
- JJ Allaire and Yihui Xie and Jonathan McPherson and Javier Luraschi and Kevin Ushey and Aron
  Atkins and Hadley Wickham and Joe Cheng and Winston Chang and Richard Iannone (2020).
  rmarkdown: Dynamic Documents for R. R package version 2.3. URL https://rmarkdown.rstudio.com.

- Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43),
  1686, https://doi.org/10.21105/joss.01686
  
- Rohan Alexander and Sam Caetano (2020). Cleaning the GSS 2017 file.

- Yihui Xie (2020). knitr: A General-Purpose Package for Dynamic Report Generation in R. R
  package version 1.28.

## Code
  
Code that supports this analysis can be found at https://github.com/matthewwankiewicz/sta304ps3